Gaussian Processes Autoregressive Models for the Disturbance Storm Time Index

### 2016-05-03 swsc.tex
Updates from ShareLaTeX

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_RMSE.png}
      \caption{Averaged RMSE}
         \label{fig:rmse}
   \end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_RelProb.png}
   \caption{Comparison of empirical distribution of relative errors for various models on the list of 63 storms in \citet{Ji2012}.}
   \label{fig:relprob}
\end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_CC.png}
      \caption{Averaged Cross correlation coefficient}
         \label{fig:cc}
   \end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_deltaDst.png}
      \caption{Averaged $\Delta Dst_{min}$}
         \label{fig:deltaDst}
   \end{figure}

\section{Results} \label{sec:res}
%%  This two-panel figure was inserted by JFW to demonstrate the subfigure and epstopdf packages
\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_timingerr.png}
      \caption{Averaged absolute timing error}
         \label{fig:timingErr}
   \end{figure}

@@

@@

>>>>

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_RMSE.png}
      \caption{Averaged RMSE performance of GP-AR, GP-ARX and the Persistence model versus results in \citet{Ji2012}.}
         \label{fig:rmse}
   \end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_RelProb.png}
   \caption{Comparison of empirical distribution of relative errors for GP-AR, GP-ARX, NM and TL on the test set of \citet{Ji2012}.}
   \label{fig:relprob}
\end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_CC.png}
      \caption{Averaged cross correlation performance of GP-AR, GP-ARX and the Persistence model versus results in \citet{Ji2012}.}
         \label{fig:cc}
   \end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_deltaDst.png}
      \caption{Averaged $\Delta Dst_{min}$ of GP-AR, GP-ARX and the Persistence model versus results in \citet{Ji2012}.}
         \label{fig:deltaDst}
   \end{figure}

\section{Results} \label{sec:res}
%%  This two-panel figure was inserted by JFW to demonstrate the subfigure and epstopdf packages

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_timingerr.png}
      \caption{Averaged absolute timing error of GP-AR, GP-ARX and the Persistence model versus results in \citet{Ji2012}.}
         \label{fig:timingErr}
   \end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Compare_pred_err_bar.png}
      \caption{OSA predictions with error bars $\pm 1$ standard deviation, generated by the GP-ARX model for the storm event $9^{th}$ November $2004$ 11:00 UTC - $11^{th}$ November $2004$ 09:00 UTC}
         \label{fig:predictionswitherrorbar}
\end{figure}
